---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gtmodels

<!-- badges: start -->
<!-- badges: end -->

The `gtmodels` R package allows you to output multiple models as a single `gt_tbl` table using the [gt](https://gt.rstudio.com/) package. This output can easily be embedded in R Markdown and Quarto documents. Furthermore, because the output is a `gt_tbl` object, it can easily be customized further by the user using standard `gt` commands. 

## Installation

You can install the development version of `gtmodels` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AaronGullickson/gtmodels")
```

## Example

This is a basic example which shows you how to build a table containing several models:

```{r example, results='hide'}
library(gt)
library(gtmodels)

# build some models
model1 <- lm(mpg ~ hp, data = mtcars)
model2 <- update(model1, . ~ . + disp + wt)
model3 <- update(model2, . ~ . + as.factor(cyl))

# create a name correspondence for final row labels
name_corr <- c("(Intercept)" = "Constant",
               "hp" = "Horsepower",
               "disp" = "Displacement (cu. in.)",
               "wt" = "Weight (1000 lbs)",
               "as.factor(cyl)6" = "6-cylinder",
               "as.factor(cyl)8" = "8-cylinder",
               "n" = "N",
               "rsquared" = "R-squared",
               "bic" = "BIC")

tbl <- gt_model(list(model1, model2, model3),
         summary_stats=c("rsquared","bic"),
         var_labels = name_corr) |>
  cols_label(model1 = "(1)", model2 = "(2)", model3 = "(3)") |>
  fmt_number(rows = c("summary:bic"), decimals = 1) |>
  tab_source_note(md("*Notes:* Standard errors shown in parenthesis."))

tbl
```

```{r raw-html, echo=FALSE}
as_raw_html(tbl)
```

